\section{Contributions}
The objective of this master's thesis was twofold, first to find or create a simulation tool able accurately simulating the behaviour of a robot in a physical world, second, to use that tool as a prototyping platform for the purpose of designing a humanoid robot able of performing actions such as standing up and walking. 

\subsection{Simulation tool}
We solved the first problem by surveying the available physics simulation software and choosing the ones we were going to use. We decided to work with a simulator instead of just a physics engines in order to begin working with simulations sooner, without spending time on re-developing features that are already present in simulators. Out of the surveyed simulators, V-Rep was chosen because it has all the desired features (joints, access to the parameters of the physics engine, remote control of the simulation) and has good reviews, as shown in a survey done by Hummel \emph{et al.} in \cite{hummel2012evaluation}. However, V-Rep is not without flaws, the biggest one being the lack of a proper mesh creation capabilities. For that reason, we chose to use Blender to create the meshes of objects we want to model. 

\subsection{Simulations}
We solved the second problem using both Blender an V-Rep to create models of the elements we deemed necessary for a complete model of a robot. Some objects were easier to model, as they do not perform any active role other than being physically present. Other necessitated the use of scripts to emulate their real-life behaviour. Such was the case of the cameras and servomotors. Fortunately V-Rep provides some basic infrastructure for the simulation of vision sensors and servomotors. Most of the work thus went into the determination of the correct parameters to use in order to produce a physically accurate simulation.

These objects were assembled together to create a complete model of the robot. Different designs were tested and each iteration brought us closer to a robot able of standing and walking which we finally created. 

\section{Problems encountered}
A master's thesis is a major endeavour and these are rarely devoid of obstacles. During this year several elements obstructed the completion of this work: \begin{itemize}
\item V-Rep is a fine tool but the lack of a proper internal modelling tool was a major thorn in the side as every major modification meant that the whole model had to be modified in Blender and re-imported into V-Rep. This created a lot of overhead work which contributed nothing of interest to this work. 

This drawback is generalized amongst all the simulators that we surveyed at the beginning of this report and we feel it should be addressed quickly by their creators. Nevertheless, we understand that a modelling tool such as Blender took years to create so we would not expect simulators to catch up any time soon.

\item We also learned of the importance of studying mechanisms carefully before using them. Though things might appear simple at first, subtle implementation details might change everything. A fine example of that is us melting the core of the motor inside a MX-28R servomotor during our tests because of our trust in the announced safety mechanisms. Needless to say, they proved insufficient and we should have examined the documentation more closely.

\item Choosing a physics engine was difficult because the field is quite fragmented. On one hand there exist well established commercial solutions, but they are focused on games and make some significant shortcuts whenever possible in order to be as fast as possible. On the other hand there exist a quantity of open-source physics engines but they are usually the work of one man and are poorly documented. It was hard to motivate the choice of Newton Dynamics on any other basis than 'it worked best'.
\end{itemize}

\section{Future work}
\subsection{Modelling}
While the model is in a usable state it could still be bettered and we suggest to begin with the items listed hereafter:
\begin{itemize}
\item \textbf{Springs.} As of now our work with springs is just a proof of concept.

\item \textbf{Inertia.} The model uses a simplified representation of inertia, in the belief that a controller should be able to correct minor differences in behaviour between the model and the actual robot. If inertia needs to be made more accurate, we suggest to use Meshlab\footnote{\url{http://meshlab.sourceforge.net/}} to compute the inertia of objects.

\item \textbf{Model format.} It is still uncertain if Blender shall continue to support the Collaborative Design Activity (COLLADA) format, as mentioned in the development roadmap (\cite{blender_roadmap}). This format has been very useful throughout this master's thesis as it made possible to import a 3D model of the robot while keeping the distinct objects of the model separate. This is not the case with other mesh formats where the imported model is a single entity that we must separate into atomic elements. 

Should the support for this format be dropped, a choice should be made whether to continue using the COLLADA format and find another modelling software that supports it, or to move on to another format. In the case the latter is chosen we suggest to use the Unified Robot Description format (URDF), basically a xml file which is supported by most of the robotics simulators we surveyed.

\end{itemize}

\subsection{Routines}
Now that we have a simulator and a complete model of the robot, more routines can be created. 
\begin{itemize}
\item \textbf{Standing up from a supine position.} Even though the robot can roll from a supine to a prone position and use the standing from prone routine, it would be faster to be able to stand from a supine position directly.

\item \textbf{Walking.} Being able to walk is the basic requirement for a robot to compete in RoboCup. A walking sequence is the last proof needed to be able to tell that the robot we designed is able to compete.

\item \textbf{Shooting a ball.} As soon as the robot is able to walk, the next step should be testing if it can shoot a soccer ball.
\end{itemize}

\subsection{Online simulation}
In parallel or after creating the aforementioned routines, the simulator should be used to test the high level control code of the robot. The interaction between the simulator and the control code would be the same as in this master's but the control code would be much more complex than the routines we created.

